---
title: "Polling Data"
author: "Marcel Schliebs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

introductory remarks

```{r,warning=FALSE}
library(voteR)
```

Scrape all available polls. 

```{r,warning = FALSE}
df <- scrape_wahlrecht_bund()
```

Explore how many polls are available in total: 
```{r}
nrow(df)
```

And split up by institute: 
```{r}
df %>% pull(institute) %>% table()
```

Check out the availbe variables: 
```{r}
colnames(df)
```

Print the first 10 observations to see an example:

```{r}
df %>% slice(1:10)
```

## Select polling institutes

Furthermore, a set of institutes to be included can be selected via a character vector passed to the `institutes` parameter. Possible options include `allensbach`, `emnid`, `forsa`, `politbarometer`, `gms`, `dimap`, `insa`, and `yougov`

```{r,warning =F}
scrape_wahlrecht_bund(institutes = c("dimap","politbarometer"))
```

## Include Unweighted Raw Data (if available)

Lastly, for some institutes (namely `Politbarometer` and `GMS`), it is also possible to include (declared) raw-data which has not been post-treated or weighted. These data points are excluded by default but can be included by using the `include_rawdata = TRUE` option. 

```{r,warning = F}
scrape_wahlrecht_bund(include_rawdata = T) %>% 
  filter(raw_by_institute == T)
```


# Visualize Polls

```{r,warning = F}
library(ggplot2)

ggpoll <- 
  df %>% 
  gather(party,pollscore,`cdu/csu`:others) %>% 
  filter(!party %in% c("others")) %>%
  ggplot(aes(x = as.Date(date,"%d.%m.%Y"),
                 y = pollscore)) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(aes(col = party)) + 
  facet_wrap(~party,scales = "free")
ggpoll
```

Restrict graph to last legislative period only:
```{r}
ggpoll2 <- 
  ggpoll + 
  scale_x_date(limits = c(as.Date("2017-09-22"),Sys.Date()))
ggpoll2
```

And adjust party colors accordingly:

```{r}
partycolors_ger <- c(spd = "red",
                     cdu = "black",
                     cdu_csu = "black",
                     `cdu/csu` = "black",
                     csu = "darkblue",
                     gruene = "darkgreen",
                     grüne = "darkgreen",
                     fdp =  "#999900",
                     afd = "blue",
                     piraten = "orange",
                     linke = "purple",
                     andere = "black",
                     sonstige = "grey")

ggpoll2 + 
  scale_color_manual(values = partycolors_ger) + 
  theme_minimal() + 
  labs(x = "Date",
       y = "Pollscore")

```

